---
title       : Great Schools Ratings by Race in Elementary Schools in Maryland USA
subtitle    : 
author      : Rich Banks
job         : GIS Analyst
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Executive Summary 

The purpose of this application was to plot a correlation between the percentage of a particular race at an elemntary school and it's school rating according to Great Schools (www.greatschools.org)

By using the application, the user will be able to display a rating summary of one or multiple school districts in Maryland by the race of a user's choice. 

Please note that this application only covers elementary schools in just a a few counties in the state of Maryland.

--- .class #id 

## The Data
The input dataset was compiled from extracting the data from the Great Schools website using an API token that I registered for. By performing queries against their database using a standard HTML request I was able to create a .csv file from extracting information from the XML files which were created as a result of the query. 
Ater much manipulation of the dataset, I was able to come up with a tidy dataset as seen below
```{r}
 schools <- read.csv("schooloutput_v2.csv")
names(schools)
 

```

These values represent the following:  "name" is the name of the school , "r" is the rating , "dis" is the district, and the last several fields are values representing the percentage of the race at that particular school

---

## The Interface

The first pull-down menu lets the user choose from different races represented in elementary schools in Maryland. The choices are : white, asian , hispanic, black, Native American, Pacific Islander and mixed race. 

The multiple-checkbox below allows the user to choose which school district to get ratings information from.

The tabs on the top-right let the user see a plot, a table summary by rating , and a complete table of the dataset based on their inputs.

---

## Sample Plot Output

```{r ,fig.width=7, fig.height=4, echo=FALSE , cache = FALSE}

library(ggplot2) 
  myd <- subset(schools, dis == "Montgomery County Public Schools"  )
  mydata <- data.frame(rating = myd$r, race = myd[,"white"] )
   ggplot(mydata, aes(x = rating, y = race)) + geom_point(color="red") + labs(x="Great Schools Rating",y="Race Percentage") 
   #qplot(rating, race, data = mydata)

```

---

## Sources

Data Source : http://www.greatschools.org

Application  : http://richisgeo.shinyapps.io/SchoolRatings/



---


